---
title: "Thinking Like a Bayesian<br>(Part 1)"
execute:
  echo: true
  warning: false
  message: false
format:
  revealjs:
    theme: simple
    css: style_lecture.css
    include-after-body: headers.html
    self-contained: true
    slide-number: true
    footer: "STA6349 · Applied Bayesian Analysis · Fall 2026"
    width: 1600
    height: 900
    df-print: kable
    html-math-method: katex
    code-fold: false
    code-tools: false
    incremental: false
editor: source
---

## Introduction

- On Monday:
    - Refresher on probability theory
    - What does each distribution do?
        - beta $\to$ outcomes limited to [0, 1]
        - binomial $\to$ binary outcomes
        - gamma $\to$ continuous & positive outcomes; skewed right
        - normal $\to$ continuous outcomes; mound-shaped & symmetric distribution
        - Poisson $\to$ count outcomes; skewed right
        - uniform $\to$ each outcome has equal probability; rectangular distribution
        
- Today: building up Bayesian analysis concepts

## R Set Up

- To follow today's lecture, please load the following packages:

```{r}
library(tidyverse)
library(janitor)
library(bayesrules)
```

- If you need to install any, you can do so with the `install.packages()` function.

```{r}
#| eval: false

install.packages("bayesrules")
```

## Thinking Like a Bayesian

- Bayesian analysis involves updating beliefs based on observed data.

```{r}
#| echo: false
library(DiagrammeR)
library(htmltools)
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = rectangle, style = rounded, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e', width = 2.5, height = 0.8,
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Incoming information:\n5 star restaurant']
}
", width = 900, height = 550)
div(style = "display: flex; justify-content: center; align-items: center;", g)
```

## Thinking Like a Bayesian

- Bayesian analysis involves updating beliefs based on observed data.

```{r}
#| echo: false
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = rectangle, style = rounded, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e', width = 2.5, height = 0.8,
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Incoming information:\n5 star restaurant']
  B [label = 'Data:\nsoggy noodles']
  C [label = 'Updated information:\n3 star restaurant']
  
  A -> C
  B -> C
}
", width = 900, height = 550)
div(style = "display: flex; justify-content: center; align-items: center;", g)
```

## Thinking Like a Bayesian

- Bayesian analysis involves updating beliefs based on observed data.

```{r}
#| echo: false
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = rectangle, style = rounded, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e', width = 2.5, height = 0.8,
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Incoming information:\n5 star restaurant']
  B [label = 'Data:\nsoggy noodles']
  C [label = 'Updated information:\n3 star restaurant']
  D [label = 'New data:\ntasty alfredo']
  E [label = 'Updated information:\n4 star restaurant']
  
  A -> C
  B -> C
  C -> E
  D -> E
}
", width = 900, height = 550)
div(style = "display: flex; justify-content: center; align-items: center;", g)
```

## Thinking Like a Bayesian

- Bayesian analysis involves updating beliefs based on observed data.

```{r}
#| echo: false

g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = rectangle, style = rounded, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e', width = 2.5, height = 0.8,
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Incoming information:\n5 star restaurant']
  B [label = 'Data:\nsoggy noodles']
  C [label = 'Updated information:\n3 star restaurant']
  D [label = 'New data:\ntasty alfredo']
  E [label = 'Updated information:\n4 star restaurant']
  F [label = 'New data:\nso-so salad']
  G [label = '...', shape = plaintext]
  
  A -> C
  B -> C
  C -> E
  D -> E
  E -> G [style = dashed]
  F -> G [style = dashed]
}
", width = 900, height = 550)

div(style = "display: flex; justify-content: center; align-items: center;", g)
```

## Thinking Like a Bayesian

- This is the natural Bayesian knowledge-building process of:
    - acknowledging your preconceptions (prior distribution),
    
```{r}
#| echo: false
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = ellipse, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e',
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Prior']
  
  A 
}
")
div(style = "display: flex; justify-content: center; align-items: center;", g)
```  
    
## Thinking Like a Bayesian

- This is the natural Bayesian knowledge-building process of:
    - acknowledging your preconceptions (prior distribution),
    - using data (data distribution) to update your knowledge (posterior distribution), 

```{r}
#| echo: false
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = ellipse, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e',
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Prior']
  B [label = 'Data']
  C [label = 'Posterior']
  
  A -> C
  B -> C
}
")
div(style = "display: flex; justify-content: center; align-items: center;", g)
```    
    

## Thinking Like a Bayesian

- This is the natural Bayesian knowledge-building process of:
    - acknowledging your preconceptions (prior distribution),
    - using data (data distribution) to update your knowledge (posterior distribution), and 
    - repeating (posterior distribution $\to$ new prior distribution)

```{r}
#| echo: false
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = ellipse, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e',
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Prior']
  B [label = 'Data']
  C [label = 'Posterior']
  D [label = 'New data']
  E [label = 'Posterior']
  F [label = 'New data']
  G [label = '', shape = point, width = 0.01]
  
  A -> C
  B -> C
  C -> E
  D -> E
  E -> G [style = dashed]
  F -> G [style = dashed]
}
")
div(style = "display: flex; justify-content: center; align-items: center;", g)
```

## Thinking Like a Bayesian 

- Bayesian and frequentist analyses share a common goal: to learn from data about the world around us. 
    - Both Bayesian and frequentist analyses use data to fit models, make predictions, and evaluate hypotheses. 
    - When working with the same data, they will typically produce a similar set of conclusions. 
    
- Statisticians typically identify as either a "Bayesian" or "frequentist" ...
    - We are not going to "take sides." 
    - We will see these as tools in our toolbox.

## Thinking Like a Bayesian
    
- **Bayesian probability:** the relative plausibility of an event. This considers prior belief.

```{r}
#| echo: false
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = ellipse, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e',
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Prior']
  B [label = 'Data']
  C [label = 'Posterior']
  
  A -> C
  B -> C
}
", width = 900, height = 550)
div(style = "display: flex; justify-content: center; align-items: center;", g)
```
    
## Thinking Like a Bayesian

- **Frequentist probability:** the long-run relative frequency of a repeatable event. This does not consider prior belief.   

```{r}
#| echo: false
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = ellipse, fontname = 'EB Garamond',
      color = '#2e2e2e', fontcolor = '#2e2e2e',
      fontsize = 18]
  edge [color = '#2e2e2e']
  
  A [label = 'Data']
}
", width = 900, height = 550)
div(style = "display: flex; justify-content: center; align-items: center;", g)
```

## Thinking Like a Bayesian

- The Bayesian framework depends upon prior information, data, and the balance between them.

    - The balance between the prior information and data is determined by the relative strength of each.

```{r}
#| echo: false
#| fig-width: 10
#| fig-height: 3
#| fig-align: 'center'
#| warning: false

trees <- tibble(
  tree   = 1:3,
  cx     = c(1.5, 4.0, 6.5),
  tilt   = c(-0.08, 0.0, 0.08),
  half_w = 0.8
)

bars <- trees |>
  mutate(
    x_prior = cx - half_w, y_prior = 0.8 - tilt,
    x_data  = cx + half_w, y_data  = 0.8 + tilt,
    y_mid   = 0.8
  )

# stem goes from BOTTOM up to bar
stems <- bars |>
  mutate(x = cx, xend = cx, y = 0.1, yend = y_mid)

drops <- bars |>
  select(tree, cx, x_prior, x_data, y_prior, y_data) |>
  pivot_longer(
    cols = c(x_prior, x_data, y_prior, y_data),
    names_to = c(".value", "side"),
    names_pattern = "(x|y)_(prior|data)"
  ) |>
  mutate(
    xend  = x,
    yend  = y - 0.35,
    label = side
  )

ggplot() +
  # stem up from bottom
  geom_segment(data = stems,
               aes(x = x, y = y, xend = xend, yend = yend),
               color = "#2e2e2e", linewidth = 1.2) +
  # bar on top
  geom_segment(data = bars,
               aes(x = x_prior, y = y_prior, xend = x_data, yend = y_data),
               color = "#2e2e2e", linewidth = 1.2) +
  # drops hanging down from bar ends
  geom_segment(data = drops,
               aes(x = x, y = y, xend = xend, yend = yend),
               color = "#2e2e2e", linewidth = 1.2) +
  # labels
  geom_label(data = drops |> distinct(x, label, .keep_all = TRUE),
             aes(x = xend, y = yend, label = label),
             family = "EB Garamond", size = 6,
             color = "#2e2e2e", fill = "#f5f3ee",
             label.padding = unit(0.4, "lines")) +
  scale_x_continuous(limits = c(0.3, 7.7)) +
  scale_y_continuous(limits = c(-0.1, 1.1)) +
  theme_void() +
  theme(plot.background = element_rect(fill = "#f5f3ee", color = NA))
```



- When we have little data, our posterior can rely more on prior knowledge. 

- As we collect more data, the prior can lose its influence.

## Thinking Like a Bayesian

- We can also use this approach to combine analysis results.

```{r}
#| echo: false
g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = ellipse, fontname = 'EB Garamond',
        color = '#2e2e2e', fontcolor = '#2e2e2e', fontsize = 20]
  edge [color = '#2e2e2e']

  A [label = 'Your prior']
  B [label = 'Your data']
  C [label = 'Your posterior']
  D [label = 'Your new data']
  E [label = 'Your new posterior']
  F [label = 'My prior']
  G [label = 'My data']
  H [label = 'My posterior']
  I [label = 'My new data']
  J [label = 'My new posterior']
  K [label = 'Our posterior']

  A -> C
  B -> C
  C -> E
  D -> E
  F -> H
  G -> H
  H -> J
  I -> J
  E -> K [style = dashed]
  J -> K [style = dashed]
}
", width = 900, height = 550)

div(style = "display: flex; justify-content: center; align-items: center;", g)
```

## Thinking Like a Bayesian

- We will use an example to work through Bayesian logic.

- The Collins Dictionary named "fake news" the 2017 term of the year. 

    - Fake, misleading, and biased news has proliferated along with online news and social media platforms which allow users to post articles with little quality control. 
    
- We want to flag articles as "real" or "fake." 

- We'll examine a sample of 150 articles which were posted on Facebook and fact checked by five BuzzFeed journalists (Shu et al. 2017). 

## Thinking Like a Bayesian

- Information about each article is stored in the `fake_news` dataset in the `bayesrules` package. 

```{r}
fake_news <- bayesrules::fake_news
print(colnames(fake_news))
```


## Thinking Like a Bayesian

- Suppose that the most recent article posted to a social media platform is titled: *The president has a funny secret!*
    - Some features of this title probably set off some red flags. 
    - For example, the usage of an exclamation point might seem like an odd choice for a real news article. 

- In the dataset, what is the split of real and fake articles?

```{r}
#| eval: false
fake_news %>% tabyl(type)
```

## Thinking Like a Bayesian

- In the dataset, what is the split of real and fake articles?

```{r}
fake_news %>% tabyl(type)
```

## Thinking Like a Bayesian

- What does the data say?

```{r}
#| eval: false
fake_news %>% tabyl(title_has_excl, type) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns()
```

## Thinking Like a Bayesian

- What does the data say?

```{r}
fake_news %>% tabyl(title_has_excl, type) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns()
```
    
- 26.67% of fake news titles use ! vs 2.22% of real news titles use !
    
## Thinking Like a Bayesian

- We now have two pieces of contradictory information. 
    - Our prior information suggested that incoming articles are most likely real. 
    - However, the exclamation point data is more consistent with fake news. 

```{r}
#| echo: false

g <- grViz("
digraph {
  graph [layout = dot, rankdir = TB, bgcolor = '#f5f3ee', fontname = 'EB Garamond']
  node [shape = ellipse, fontname = 'EB Garamond',
        color = '#2e2e2e', fontcolor = '#2e2e2e', fontsize = 22]
  edge [color = '#2e2e2e']

  A [label = 'Prior:\n40% of articles are fake.']
  B [label = 'Data:\n! more common among fake news.']
  C [label = 'Posterior:\nUmmmmmm....']

  A -> C
  B -> C
}
", width = 900, height = 550)

div(style = "display: flex; justify-content: center; align-items: center;", g)
```

## Building a Bayesian Model

- Thinking like Bayesians, we know that balancing both pieces of information is important in developing a posterior understanding of whether the article is fake.

- Our fake news analysis studies two variables: 
    - an article's fake vs real status and 
    - its use of exclamation points. 
    
- We can represent the randomness in these variables using probability models. 

## Building a Bayesian Model

- Let's now formalize our prior understanding of whether the new article is fake. 

- Based on our data, we saw that 40% of articles are fake and 60% are real.

    - Before reading the new article, there’s a 0.4 *prior* probability that it's fake.
    
$$P\left[B\right] = 0.40 \text{ and } P\left[B^c\right] = 0.60$$    

- Remember that a valid probability model must: 

    1. account for all possible events 
    2. assign prior probabilities to each event
    3. have probabilities that sum to 1
    
## Building a Bayesian Model

- Revisiting the contingency table for conditional probabilities,
    
```{r}
#| echo: false
fake_news %>% tabyl(title_has_excl, type) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns() 
```       

- If an article is fake ($B$), what is the probability that it uses exclamation points in the title?  <br><br><br><br>

- If an article is real ($B^c$), what is the probability that it uses exclamation points in the title?
    
## Building a Bayesian Model

- We have the following conditional probabilities:
    - If an article is fake, then there is about a 27% chance it uses exclamation points in the title.
        - $P[A|B]=0.2667$
    - If an article is real, then there is only a 2% chance it uses exclamation points in the title. 
        - $P[A|B^c]=0.0222$

- Exclamation point usage is much more likely among fake news than real news.
    - We have evidence that the article is fake.    
    
## Building a Bayesian Model

- Note that we know that the incoming article used exclamation points ($A$), but we do not actually know if the article is fake ($B$ or $B^c$).

- In this case, we compared $P[A|B]$ and $P[A|B^c]$ to ascertain the **relative likelihood** of observing $A$ under different scenarios. That is,
    - $L\left[B|A\right] = P\left[A|B\right]$ $\to$ the likelihood of fake given !
    - $L\left[B^c|A\right] = P\left[A|B^c\right]$ $\to$ the likelihood of real given !

## Building a Bayesian Model

| Event | *B* | *B^c^* | Total |
|--|:--:|:--:|:--:|
| Prior Probability | 0.4 | 0.6 | 1.0 |
| Likelihood | 0.2667 | 0.0222 | 0.2889 |

$$L\left[B|A\right] = P\left[A|B\right] \text{ and } L\left[B^c|A\right] = P\left[A|B^c\right]$$

- It is important for us to note that the likelihood function is *not* a probability function.
    - This is a framework to determine the relative compatibility of our exclamation point data with $B$ and $B^c$.

## Building a Bayesian Model

| Event | *B* (fake) | *B^c^* (real) | Total |
|--|:--:|:--:|:--:|
| Prior Probability | 0.4 | 0.6 | 1.0 |
| Likelihood | 0.2667 | 0.0222 | 0.2889 |

- The prior evidence suggested the article is most likely real,

$$P[B] = 0.4 < P[B^c] = 0.6$$

- The data, however, is more consistent with the article being fake,

$$L[B|A] = 0.2667 > L[B^c|A] = 0.0222$$

## Building a Bayesian Model

- We can summarize our probabilities in a table, 

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       |     |       |       |
| $A^c$     |     |       |       |
| **Total** | 0.4 | 0.6   | 1     |

- As found earlier, $P[A|B] = 0.2667$ and $P[A|B^c]=0.0222$.

- Find $P[A \cap B]$.

## Building a Bayesian Model

- We can summarize our probabilities in a table, 

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       |     |       |       |
| $A^c$     |     |       |       |
| **Total** | 0.4 | 0.6   | 1     |

- As found earlier, $P[A|B] = 0.2667$ and $P[A|B^c]=0.0222$.

$$
\begin{align*}
P[A \cap B] &= P[A|B] \times P[B] \\
&= 0.2667 \times 0.4 \\
&= 0.1067
\end{align*}
$$


## Building a Bayesian Model

- Here's what we know,

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067    |       |       |
| $A^c$     |     |       |       |
| **Total** | 0.4 | 0.6   | 1     |

- As found earlier, $P[A|B] = 0.2667$ and $P[A|B^c]=0.0222$.

- Find $P[A^c \cap B]$.

## Building a Bayesian Model

- Here's what we know,

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067    |       |       |
| $A^c$     |     |       |       |
| **Total** | 0.4 | 0.6   | 1     |

- As found earlier, $P[A|B] = 0.2667$ and $P[A|B^c]=0.0222$.

$$
\begin{align*}
P[A^c \cap B] &= P[A^c|B] \times P[B]  \\
&= \left(1-P[A|B]\right) \times P[B] \\
&= (1-0.2667) \times 0.4 \\
&= 0.2933
\end{align*}
$$

## Building a Bayesian Model

- Here's what we know,

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067 |       |       |
| $A^c$     | 0.2933 |       |       |
| **Total** | 0.4 | 0.6   | 1     |

- As found earlier, $P[A|B] = 0.2667$ and $P[A|B^c]=0.0222$.

- Find $P[A \cap B^c]$.

## Building a Bayesian Model

- Here's what we know,

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067 |       |       |
| $A^c$     | 0.2933 |       |       |
| **Total** | 0.4 | 0.6   | 1     |

- As found earlier, $P[A|B] = 0.2667$ and $P[A|B^c]=0.0222$.

$$
\begin{align*}
P[A \cap B^c] &= P[A|B^c] \times P[B^c]  \\
&= 0.0222 \times 0.6 \\
&= 0.0133
\end{align*}
$$

## Building a Bayesian Model

- Here's what we know,

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067 | 0.0133 |       |
| $A^c$     | 0.2933 |       |       |
| **Total** | 0.4 | 0.6   | 1     |

- As found earlier, $P[A|B] = 0.2667$ and $P[A|B^c]=0.0222$.

 - Find $P[A^c \cap B^c]$.
 
## Building a Bayesian Model

- Here's what we know,

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067 | 0.0133 |       |
| $A^c$     | 0.2933 |       |       |
| **Total** | 0.4 | 0.6   | 1     |

- As found earlier, $P[A|B] = 0.2667$ and $P[A|B^c]=0.0222$.

$$
\begin{align*}
P[A^c \cap B^c] &= P[A^c|B^c] \times P[B^c]  \\
&= 0.9778 \times 0.6 \\
&= 0.5867
\end{align*}
$$

## Building a Bayesian Model

- Here's what we know,

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067 | 0.0133 |       |
| $A^c$     | 0.2933 | 0.5867 |       |
| **Total** | 0.4 | 0.6   | 1     |

- Finally,

$$
\begin{align*}
&P[A] = 0.1067 + 0.0133 = 0.12 \\
&P[A^c] = 0.2933 + 0.5867 = 0.88
\end{align*}
$$

## Building a Bayesian Model

- Using rules of probability, we have completed the table.

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067 | 0.0133 | 0.12 |
| $A^c$     | 0.2933 | 0.5867 | 0.88 |
| **Total** | 0.4 | 0.6   | 1     |

## Building a Bayesian Model

- With more information, we can finally find the probability that the latest article is fake.

- We will use the posterior probability, $P[B|A]$, which is found using Bayes' Rule.

- **Bayes' Rule**: For events $A$ and $B$, 

$$P[B|A] = \frac{P[A \cap B]}{P[A]} = \frac{P[B] \times L[B|A]}{P[A]}$$

- But really, we can think about it like this,

$$\text{posterior} = \frac{\text{prior} \times \text{likelihood}}{\text{normalizing constant}}$$

## Building a Bayesian Model

- Let's now apply Bayes' Rule to our fake news example.

|           | $B$ | $B^c$ | Total |
|-----------|:---:|:-----:|:-----:|
| $A$       | 0.1067 | 0.0133 | 0.12 |
| $A^c$     | 0.2933 | 0.5867 | 0.88 |
| **Total** | 0.4 | 0.6   | 1     |

- Find $P[B|A]$.

## Building a Bayesian Model

- Applying Bayes' Rule to our fake news example,

$$P[B|A] = \frac{P[A \cap B]}{P[A]} = \frac{0.1067}{0.12} = 0.889$$

- There is an 88.9% posterior probability that the article is fake given that it uses an exclamation point in the title.

## Building a Bayesian Model

- Comparing our prior and posterior probabilities,
    - **Prior:** $P[B] = 0.40$, i.e., before seeing the title, 40% chance the article is fake.
    - **Posterior:** $P[B|A] = 0.889$, i.e., after seeing the exclamation point in the title, 88.9% chance the article is fake.

- The exclamation point adds strong evidence to the article being fake. 
    - Our posterior is much higher than our prior.

## Wrap Up

- Today we have introduced thinking like a Bayesian.

- The biggest take away: we now consider prior data/beliefs, rather than just the collected data.

- Next week: formalizing the Bayesian model with conjugate families.

    - Beta-Binomial
    
    - Gamma-Poisson
    
    - Normal-Normal



